SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-03 docs/questioning.tex
work on the hybrid category

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).
{\it {\sc sm}ask}~\cite{JB07} is another framework
that was inspired by {\sc isr}. To detect {\sc xss}
attacks it searches for {\sc html} and JavaScript
keywords within the application's legitimate code.
This is done before the processing of an {\sc http}
request. When it finds one it adds a token to it.
This results to a ``code mask". Then,
before sending the resulting {\sc html} data to the
web user, the framework searches the data for
illegal code by using the same keywords.
Since all legitimate code has been ``masked",
the injected code can be identified.
The pre- and post-processing of the code though,
may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask
did not provide measurements regarding the
computational performance of the tool (see Table~\ref{tab:comp}).

@@

{\sc xss-guard}~\cite{BV08}
maps legitimate scripts to {\sc http} responses.

{\it Blueprint}~\cite{LV09}.

>>>>

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).
{\it {\sc sm}ask}~\cite{JB07} is another framework
that was inspired by {\sc isr}. To detect {\sc xss}
attacks it searches for {\sc html} and JavaScript
keywords within the application's legitimate code.
This is done before the processing of an {\sc http}
request. When it finds one it adds a token to it.
This results to a ``code mask". Then,
before sending the resulting {\sc html} data to the
web user, the framework searches the data for
illegal code by using the same keywords (locus {\sc y}).
Since all legitimate code has been ``masked",
the injected code can be identified.
The pre- and post-processing of the code though,
may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask
did not provide measurements regarding the
computational performance of the tool (see Table~\ref{tab:comp}).

@@

This category includes mechanisms that borrow
characteristics from more than one of the above categories.

{\sc xss-guard}~\cite{BV08} is a training scheme
that also employs parse-tree validation.
During training, the scheme maps legitimate scripts
to {\sc http} responses. During production
{\sc xss-guard} retrieves for every script included
in a response its parse-tree and checks if it
is one of those previously mapped to this response.
Apart from the  comparison of the parsed-trees, {\sc xss-guard}
checks also for an exact match of lexical entities.
To achieve this, the scheme utilizes that data structures
of Firefox's JavaScript engine (locus {\sc x}).
However, string literals are not compared literally
thus, a possible false negative result could occur if an
adversary performed a mimicry attack~\cite{WS02}.
For example, consider a banner rotator that
every time it runs, it creates a value that depends on
the current date and the length of the array that
contains the references of the various images to be displayed.
Then, based on this value it shows a specific
image to a user. In a vulnerable web site that allows
users to post data and contains this banner
rotator, a malicious user could create and store a script
that has the same code structure, with the same JavaScript
keywords like the above. In this script the
attacker could also include references to tiny
images hosted on a web server that is maintained by him in order
to retrieve the {\sc ip} addresses of the
users that visit the vulnerable site.

{\it Blueprint}~\cite{LV09} is a policy
enforcement mechanism that also utilizes parsed-trees.
